---
title: "Project"
author: "Ramsai Jagadish 20243"
date: "25/03/2021"
output:
  html_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
---

### Dataset: Australian weather report from 10years.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### packages loaded.
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(corrplot)
library(broom)
```

```{r}
data <- read.csv("weatherAUS.csv")
attach(data)
dim(data) 
data <- data[complete.cases(data),]
sum(is.na(data))
nrow(data)
```
### dataset loaded and NA values removed - 56420 rows.

```{r}
summary(data)
str(data)
names(data)
```
```{r}
data[data$RainToday == "No",]$RainToday <- 0
data[data$RainToday == "Yes",]$RainToday <- 1
data[data$RainTomorrow == "Yes",]$RainTomorrow <- 1
data[data$RainTomorrow == "No",]$RainTomorrow <- 0
head(data)
```
```{r}
data$RainToday <- as.integer(data$RainToday)
data$RainTomorrow <- as.integer(data$RainTomorrow)
str(data)
```


```{r}
moddata <- read.csv("weatherAUS.csv")
names(moddata)
date <- as.Date(moddata$Date,"%d-%m-%y")
fix(date)
```

```{r}
#?plot()
plot(moddata$MaxTemp ~ date,type="o",col="lightblue", axes=F)
box()
axis(1,date,format(date,"%d-%y"))
```

```{r}
plot(moddata$Evaporation~date,type="o",col="blue",axes=F)
box()
axis(1,date,format(date,"%m-%y"))
```



### EDA

## Mintemp vs Rainfall
```{r}
ggplot(data=data, aes(x = MinTemp ,y = Rainfall))+ geom_point()
```

## Maxtemp vs Rainfall
```{r}
ggplot(data=data, aes(x = MaxTemp ,y = Rainfall))+ geom_point()
```

## Evaporation vs Rainfall
```{r}
ggplot(data=data, aes(x = Evaporation ,y = Rainfall))+ geom_point()

```

## Windgustspeed vs Rainfall
```{r}
ggplot(data=data, aes(x = WindGustSpeed ,y = Rainfall))+ geom_point()
```

## Winspeed9am windspeed3pm vs rainfall
```{r}
ggplot(data=data, aes(x = WindSpeed9am ,y = Rainfall))+ geom_point()
ggplot(data=data, aes(x = WindSpeed3pm ,y = Rainfall))+ geom_point()
```

## Humidity9am humdity3pm vs Rainfall
```{r}
ggplot(data=data, aes(x = Humidity9am ,y = Rainfall))+ geom_point()
ggplot(data=data, aes(x = Humidity3pm ,y = Rainfall))+ geom_point()
```

## Pressure9am Pressure3pm vs Rainfall
```{r}
ggplot(data=data, aes(x = Pressure9am ,y = Rainfall))+ geom_point()
ggplot(data=data, aes(x = Pressure3pm ,y = Rainfall))+ geom_point()
```

## cloud9am cloud3pm vs Rainfall
```{r}
ggplot(data=data, aes(x = Cloud9am ,y = Rainfall))+ geom_point()
ggplot(data=data, aes(x = Cloud3pm ,y = Rainfall))+ geom_point()
```

## Temp9am Temp3pm vs Rainfall
```{r}
ggplot(data=data, aes(x = Temp9am ,y = Rainfall))+ geom_point()
ggplot(data=data, aes(x = Temp3pm ,y = Rainfall))+ geom_point()
```

### outliers: Boxplot
```{r}
boxplot(MinTemp,MaxTemp, xlab="MinTemp and MaxTemp" ,ylab="span" ,col="lightblue")

boxplot(WindSpeed9am,WindSpeed3pm,xlab="WindSpeed9am and WindSpeed3pm" ,ylab="span" ,col="lightblue")

boxplot(Humidity9am,Humidity3pm ,xlab="Humidity9am and Humdity3pm" ,ylab="span" ,col="lightblue")

boxplot(Pressure9am, Pressure3pm, xlab="Pressure9am and pressure3pm" ,ylab="span" ,col="lightblue")

boxplot(Cloud9am,Cloud3pm, xlab="Cloud9am and Cloud3pm" ,ylab="span" ,col="lightblue")

boxplot(Temp9am , Temp3pm ,xlab="temp9am and temp3pm" , ylab="span", col="lightblue")

```

## Correlation Plot
```{r}
corrdata <- subset( data, select = -c(Date,Location,WindGustDir,WindDir9am,WindDir3pm,RainToday,RainTomorrow ) )
                            # removing unnecessary and categorical variables.
head(corrdata)
corrplot(cor(corrdata),
  method = "pie",
  type = "upper" # show only upper side
)
```
